\subsection{Smart-contract implementation}

\subsubsection{Accounts}

There are 2 kinds of accounts:
\begin{itemize}
  \item Personal: created for each client, directly belongs to that client;
  \item Robot: created by client, doesn't belong directly to that client (and anyone else); represents smart contract.
\end{itemize}

Robot account should contain, aside from token mapping:
\begin{itemize}
  \item Data storage for smart contract state;
  \item The code to control the account, compiled to Plutus Core language.
\end{itemize}

The Plutus Core language allows declaring a module with exported (public) methods.
These methods will be the public API for the account.

One can evaluate the Plutus Core code itself (not just call public methods) if account directly belongs to her.
Personal accounts don't have any persistent associated code to control them.

\subsubsection{Scripting}

The Plutus language will be used to program Robot nodes.
Any interaction with account is done via Plutus code.

The evaluation cost is collected and summed into Fee.

``Sandbox run'' can be performed, to check costs and programming errors.

We will call natively-implemented functions to be called from Plutus Core ``NIFs''.

Each atomic step of execution has an invocation cost.

\subsubsection{NIFs}

NIF is an action to be invoked on Account.
NIF is the only source of changes in Account.

Any operation on the Account to be implemented should be represented as a call to NIF OR as a sequence of NIF-calls.
This will allow us to reason about security/validity of operations with more confidence and limit the access and scope of each operation.

\subsubsection{Transaction}

We will cover ``simple money transfer'' and ``data disclosure'' transactions in this section.

``Simple money transfer'' transactions will be implemented as transactions with empty ``function call'' field.

Transferral transaction must contain:
\begin{itemize}
  \item Sender signature;
  \item Receiver signature;
  \item Amount and kind of funds transferred (must be non-zero overall);
  \item ``Nonce'' to prevent double-invocation.
  \item (Optional) textual message for the receiver;
  \item (Optional) function call to be invoked upon transaction approval.
  \item Digest of all other fields, encrypted with Sender private key.
\end{itemize}

Transaction is the only way for accounts to interact.

Function call (if present) will contain the name of exported function and arguments to be supplied upon invocation.

The function would be invoked like that:

\begin{verbatim}
function-name(Sender-signature, amount, value1, value2, ..., valueN)
\end{verbatim}

On successful code invocation, money will be transmitted to the Target account and the costs will be demanded from the Sender.
If the code fails, the transaction is not published as successful and is rejected.

If there is not enough money supplied for the operation or the code raised an error, whole transaction will fail.

If there is no function call in a transaction, the code invocation is assumed successful.

The \verb|Gas| fee for transaction approval will be calculated as sum of costs for atomic actions performed.

\subsubsection{Implementation of the data disclosure protocol using Robot account}

We assume that we have 2 sides:
\begin{itemize}
  \item Buyer
  \item Seller.
\end{itemize}

``Gas'' below is the estimation of the operation cost. The name and the idea are taken from Ethereum.
``Fee'' is a forfeit to either side trying to deceive the opponent.
``Sum'' is the price of the data to be sold.

Robot would work as follows. The Buyer invokes a transaction which runs code directly on his account, that constructs a robot with the following exported methods:

\begin{itemize}
  \item \begin{verbatim} start-trade(); \end{verbatim}
  \item \begin{verbatim} accept-encrypted(encrypted-mroot, size); \end{verbatim}
  \item \begin{verbatim} send-encrypted-secret(encrypted-secret); \end{verbatim}
  \item \begin{verbatim} handshake(); \end{verbatim}
  \item \begin{verbatim} reject(sk, block, proof-enc); \end{verbatim}
  \item \begin{verbatim} cancel(), \end{verbatim}
\end{itemize}
carrying \verb|Sum + Fee + Gas| amount of currency and some \verb|predicate| to check the data if applicable.

This robot is initialized with the following data:
\begin{itemize}
  \item Cost in tokens;
  \item Size of the encrypted data;
  \item Merkle tree root of encrypted data;
  \item Timeout, after which the account is destroyed;
  \item Sink, a person whom the remaining money will be send on timeout;
  \item Destructor, a procedure to invoke on timeout.
\end{itemize}

Here is the state machine of that Robot-account:

\begin{verbatim}
  (0) Account has just been created.
    "start-trade" from Seller
      WHEN transferred amount = Fee
        Notify Buyer
        AND GOTO 1

  (1) The trade is started.
    "accept-encrypted(encrypted-mroot, size)" from Buyer
      IF encrypted Merkle root and size are the same as initially set in Robot state,
        GOTO 2
      ELSE
        GOTO 8

    Timeout!
      GOTO 8

  (2) Data was transferred. Seller encrypts a session key with the Buyer's public key.
    "send-encrypted-secret(encrypted-secret)" from Seller
    Notify Buyer

  (3) Off the band, the symmetric key is sent.
    "reject(sk, block, encrypted-proof)" from Buyer
      GOTO 4

    "handshake" from Buyer
      GOTO 5

    Timeout!
      GOTO 6

  (4) Arbitration.
    The robot performs check.
    If it finds that Buyer is right (block invalidates proofs OR the predicate fails),
      GOTO 7
    else if Seller is right
      GOTO 6

  (5) Cleanup I.
    (Sum + Fee) is sent to Seller.
    GOTO 7

  (6) Cleanup II.
    All remaining money is sent to Seller.
    The account is closed.

  (7) Cleanup III.
    All remaining money is sent to Buyer.
    The account is closed.

  (8) Cleanup VI.
    Fee is sent to Seller.
    GOTO 7

\end{verbatim}

\subsubsection{Example}

Lets assume there are:
\begin{itemize}
  \item Seller, which has declared that he has his students' Linear Algebra marks for Nov, 2018 worth 500 tokens (signed in some private Merkle tree);
  \item Buyer, which has 600 tokens available.
  \item Robot, which is a smart account created by the Buyer.
\end{itemize}

We will consider three cases:
\begin{itemize}
  \item Seller sends nothing at all;
  \item Seller tried to send Buyer encrypted garbage instead of data;
  \item Buyer tried to blame Seller in giving her invalid data with data being completely valid (in terms of proofs and predicate).
\end{itemize}

All trades will have same initial part, so we will branch when nessessary.
The trades will go as follows:
\begin{itemize}
  \item The Buyer formulates a predicate to check that data corresponds its description OR uses universal truth as predicate.
  \item The Buyer requests the data from the Seller.
  \item The Seller notifies the Buyer of the data price (500 tokens).
  \item The Buyer creates a Robot using the scheme above with 500 tokens and the predicate.
  \item The Seller accepts the trade and sends \verb|start-trade()| to the Robot along with 20 tokens Fee.

  \begin{enumerate}
    \item Seller sends badly sized data or the Merkle root of the encrypted data does not match:
      \begin{itemize}
        \item The size or the Merkle root of the transferred data is invalid.
        \item The trade is stalled until time is out.
        \item On timeout the trade is reverted and money is returned to Buyer.
      \end{itemize}
    \item Seller tries to send garbage or one of blocks decrypts to garbage:
      \begin{itemize}
        \item Buyer finds that at least one block is invalid in either form.

        \item She invokes \verb|reject(sk, block, encrypted-proof)| to start arbitration.

        \item Robot checks that block falsifies proofs and that Buyer was right.

        \item Robot returns all remaining funds to Buyer.
      \end{itemize}
    \item Buyer tries to blame Seller with valid data:
      \begin{itemize}
        \item Buyer selects the block to call ``invalid''.

        \item Then she invokes \verb|reject(unencrypted-block, proof)| to start arbitration.

        \item Robot performs \verb|check-block-and-proof(block, proof)| and finds that Buyer was not right.

        \item Then it sends all 520 tokens to Seller.
      \end{itemize}
    \item Buyer receives the data and the key, but remains silent:
      \begin{itemize}
        \item If the timeout has expired, 520 tokens are sent to Seller.
      \end{itemize}
  \end{enumerate}

\end{itemize}
